{\it E}nKCF: Ensemble of Kernelized Correlation Filters for Object Tracking in High Speed

### 2017-05-02 bmvc_review.tex
Revised the KCF section partially.

\subsection{Kernelized Correlation Filter} \label{sec:kcf}
The Kernelized Correlation Filter tracker has recently been
increasingly popular due to its operation at hundreds of frames per
second with state-of-the-art tracking capabilities even in challenging
cases \cite{henriques2012exploiting,henriques2015high}. Its computational efficiency arises from its use of the
discrete Fourier transform of the circulant matrix and frequency
domain. The KCF tracker minimizes the regularized ridge regression function shown below.
\begin{equation}
E(h) = \frac{1}{2}||y-\sum_{c=1}^{C}h_{c}*x_{c}||^{2} + \frac{\lambda}{2}\sum_{c=1}^{C}||h_{c}||^{2}
\label{eq:Closedform_RidgeReg}
\end{equation}
where $y$ represents the desired continuous response whereas $h$ and
$x_{c}$ represents the learned correlation filter and training
template for the given channel. The $c$ parameter included in
\cite{henriques2015high,galoogahi2013multi} makes it possible to
integrate multi-channel features such as HoG and color into the ridge
regression function. The closed-form solution for the
eq.~\ref{eq:Closedform_RidgeReg} can be obtained by setting the
derivative of $E$ w.r.t $w$ to $0$. 
\begin{comment}The primal solution in the
frequency domain is formulated as
%\begin{equation}
%w = (X^{T}X+\lambda)^{-1}y
%\label{eq:SpatialSolution}
%\end{equation}
\begin{equation}
w = (X^{H}X+\lambda I)^{-1}X^{T}y
\label{eq:FourierSolution}
\end{equation}
where $X^{H}$ and $\lambda$represent the complex-conjugate of training
samples and regularization term. More documentation on the spatial and
Fourier domain solutions can be found in \cite{henriques2015high}. The
MOSSE tracker uses one training sample centered at estimated position
of the target. This framework does not include enough background
information into the learned model,$w$. The application of the
circulant matrix theorem into the eq.~\ref{eq:Closedform_RidgeReg}
makes it possible to include many background patches at a similar
computational complexity. A circulant matrix includes the circularly
shifted patches of the positive training sample $x$ by a cyclic shift
operator.

%By applying shifting operation to the base sample, we can generate the circulant
%matrix as
%\begin{equation}
%C = Px.
%\label{eq:CirculantMatrixGeneration}
%\end{equation}
%The circulant matrix of a base sample $x$ can be interpreted as the
%rows of a training matrix $X$ where each row represents features of a
%training sample. Mathematically, this can be written as
%\begin{equation}
%X = C(x)
%\label{eq:CIrculantMatrixTrainingData}
%\end{equation}

In this form, the equation \ref{eq:FourierSolution} could prohibit us
from implementing a high speed object tracking as we need to perform
large number of element-wise division and multiplication
operations. However, we know from \cite{gray2006toeplitz} that all
circulant matrices are represented diagonally by the Fourier Transform
regardless of the base sample $x$.
%\begin{equation}
%X = Fdiag(\hat{x})F^{H},
%\label{eq:CirculantMatrixDFT}
%\end{equation}
%where $F$ denotes a constant Fourier Transform matrix and $x$ is the
%Discrete Fourier Transform of the base sample $x$. 
%To simplify the
%cost function formulation in eq.~\ref{eq:FourierSolution} we multiply
%$X$ in eq.~\ref{eq:CirculantMatrixDFT} with $X^{H}$ yielding
%\begin{equation}
%X^{H}X = Fdiag(\hat{x}^{*}\odot \hat{x})F^{H}.
%\label{eq:SimplificationX} 
%\end{equation}
\end{comment}
Then, the Circulant-matrix based solution vector in the Fourier domain $\hat{w}$ is formulated as
\begin{equation}
\hat{w} = \hat{x}^{*}*\hat{y}(\hat{x}^{*}*\hat{x}+\lambda)^{-1}.
\label{eq:DiagonalizedPrimalSolution}
\end{equation}
To further improve the robustness to geometric and photographic variations, one can exploit non-linear
regression function in the Correlation Filter framework \cite{henriques2015high}. 
%\begin{equation}
%\alpha = y(K+\lambda I)^{-1}
%\end{equation}
%where $K$ and $\alpha$ represent the kernel matrix and corresponding
%dual space solution. 
%\cite{henriques2015high} states that kernel
%matrices is circulant for datasets of circular cylic satisfying the
%following theorem.
%\begin{equation}
%k(x,x^{'}) = k(Mx,Mx^{'}),
%\label{eq:KernelCirculantTheorem}
%\end{equation}
%where $M$ represents the permutation matrix. Some kernels satisfying
%the eq.~\ref{eq:KernelCirculantTheorem} are \textit{Gaussian},
%\textit{Polynomial}, \textit{Intersection} and \textit{Hellinger}
%kernels. 
The diagonalized Fourier domain dual form solution can be
expressed as
\begin{equation}
\hat{\alpha} = \hat{y}(\hat{k}^{xx}+\lambda)^{-1}
\label{eq:FourierDualDomainSolution}
\end{equation}
where $\hat{k}^{xx}$ represents the first row of the Kernel matrix $K$
known as \textit{gram matrix} and it is expressed as
\begin{equation}
k^{xx^{'}} = exp(-\dfrac{1}{\alpha^{2}}(||x||^{2}+||x^{'}||^{2}-2F^{-1}(\sum^{C}_{c}\hat{x}_{c}^{*}\odot \hat{x}_{c}^{'}))).
\label{eq:GaussianCorrelationSingleChannel}
\end{equation}
%\begin{equation}
%k^{xx^{'}} = exp(-\dfrac{1}{\alpha^{2}}(||x||^{2}+||x^{'}||^{2}-2F^{-1}(\hat{x}^{*}\odot \hat{x}^{'})))
%\label{eq:GaussianCorrelationSingleChannel}
%\end{equation}
The first correlation filter based trackers used grayscale feature ($C=1$) to
learn the solution vector $w$, however, multi-channel features
such as HoG and Color were later exploited to improve tracking
accuracy \cite{henriques2015high,galoogahi2013multi,tang2015multi,ma2015long,bibi2015multi}. 
\begin{comment}The multi-channel feature integration into the Gaussian Kernelization
function in eq.~\ref{eq:GaussianCorrelationSingleChannel} is achieved
in a very straight-forward way by summing the correlation result over the channels.

>>>>

\subsection{Kernelized Correlation Filter} \label{sec:kcf}
The Kernelized Correlation Filter is a well, known single target
tracking method and thetheory and its workflowhas been detailed in
other papers already
\cite{henriques2012exploiting,henriques2015high}. This section briefly
goes over the parts of the KCF relevantto thisstudy. Its
computational efficiency arises from its use of the discrete Fourier
transform of the circulant matrix and frequency domain. The KCF
essentially solves the problem of a regression in the form of the
regularized ridge regression as:
\begin{equation}
E(h) = \frac{1}{2}||y-\sum_{c=1}^{C}h_{c}*x_{c}||^{2} + \frac{\lambda}{2}\sum_{c=1}^{C}||h_{c}||^{2}
\label{eq:Closedform_RidgeReg}
\end{equation}
where $y$ represents the desired continuous response whereas $h$ and
$x_{c}$ represents the learned correlation filter and training
template for the given channel. The parameter $c$ enabled one to
integrate features in multiple channels, such as HoG and color, in
this setup \cite{henriques2015high,galoogahi2013multi}. A closed-form
solution for Equaiton \ref{eq:Closedform_RidgeReg} is available by
taking the derivative of $E$ w.r.t $w$ to $0$. To make this
closed-form solution with

Then, the Circulant-matrix based solution vector in the Fourier domain
$\hat{w}$ is formulated as
\begin{equation}
\hat{w} = \hat{x}^{*}*\hat{y}(\hat{x}^{*}*\hat{x}+\lambda)^{-1}.
\label{eq:DiagonalizedPrimalSolution}
\end{equation}
To further improve the robustness to geometric and photographic variations, one can exploit non-linear
regression function in the Correlation Filter framework \cite{henriques2015high}. 
%\begin{equation}
%\alpha = y(K+\lambda I)^{-1}
%\end{equation}
%where $K$ and $\alpha$ represent the kernel matrix and corresponding
%dual space solution. 
%\cite{henriques2015high} states that kernel
%matrices is circulant for datasets of circular cylic satisfying the
%following theorem.
%\begin{equation}
%k(x,x^{'}) = k(Mx,Mx^{'}),
%\label{eq:KernelCirculantTheorem}
%\end{equation}
%where $M$ represents the permutation matrix. Some kernels satisfying
%the eq.~\ref{eq:KernelCirculantTheorem} are \textit{Gaussian},
%\textit{Polynomial}, \textit{Intersection} and \textit{Hellinger}
%kernels. 
The diagonalized Fourier domain dual form solution can be
expressed as
\begin{equation}
\hat{\alpha} = \hat{y}(\hat{k}^{xx}+\lambda)^{-1}
\label{eq:FourierDualDomainSolution}
\end{equation}
where $\hat{k}^{xx}$ represents the first row of the Kernel matrix $K$
known as \textit{gram matrix} and it is expressed as
\begin{equation}
k^{xx^{'}} = exp(-\dfrac{1}{\alpha^{2}}(||x||^{2}+||x^{'}||^{2}-2F^{-1}(\sum^{C}_{c}\hat{x}_{c}^{*}\odot \hat{x}_{c}^{'}))).
\label{eq:GaussianCorrelationSingleChannel}
\end{equation}
%\begin{equation}
%k^{xx^{'}} = exp(-\dfrac{1}{\alpha^{2}}(||x||^{2}+||x^{'}||^{2}-2F^{-1}(\hat{x}^{*}\odot \hat{x}^{'})))
%\label{eq:GaussianCorrelationSingleChannel}
%\end{equation}
The first correlation filter based trackers used grayscale feature ($C=1$) to
learn the solution vector $w$, however, multi-channel features
such as HoG and Color were later exploited to improve tracking
accuracy \cite{henriques2015high,galoogahi2013multi,tang2015multi,ma2015long,bibi2015multi}. 
\begin{comment}The multi-channel feature integration into the Gaussian Kernelization
function in eq.~\ref{eq:GaussianCorrelationSingleChannel} is achieved
in a very straight-forward way by summing the correlation result over the channels.
